Matching Bullets

### 2015-11-30 imaging-paper.Rnw
extending discussion on dealing with break-offs

Using (for now) a single crosscut across the surface, we extract the values and remove the class characteristics using a loess fit as before. This enables us to focus on the individual characterists. Striation marks show up in this representations as peaks and valleys. Figure~\ref{fig:cross100} shows lines of the surface crosscut at $x = 100$. A horizontal shift of one of the lines (result shown in (b)) emphasizes the strong similarities.
\hh{This horizontal shift is based on the cross-correlation between the two surface crosscuts. Let $f(t)$ and $g(t)$ define the values of the crosscut at $t$, then the cross-correlation between $f$ and $g$ at lag $k$ is defined as
\[
(f * g) (k) = \sum_t f(t+k) g(t),
\]
with suitable defined limits of the summation. % (because variances of $f$ and $g$ do not change, the above equation is proportional to the correlation). 
}
\begin{figure}
<<ccf, echo=FALSE, fig.width = 7, fig.height = 3, out.width = '\\linewidth'>>=
lag <- ccf$lag[which.max(ccf$acf)]
qplot(x=ccf$lag, xend=ccf$lag, y = 0, yend= ccf$acf, geom="segment", colour = I("grey50")) + 
  theme_bw() + ylab("Correlation") + xlab("Lag k") +
  geom_segment(aes(x = lag, xend = lag, y = 0, yend =  max(ccf$acf)), colour="black") + 
  scale_x_continuous(breaks = c(-100, -50, lag, 0, 50, 100),
                     minor_breaks = c(-75,-25,25, 75))
@
\caption{\label{fig:ccf}Cross-correlation between the two crosscuts shown in Figure~\ref{fig:crosscut} at lags between -100 and 100. At a lag of -10 the correlation peaks, indicating the largest amount of agreement between the crosscuts. Figure~\ref{fig:crosscutX} shows the lag-shifted crosscuts.}
\end{figure}

@@

\hh{Figure~\ref{fig:match} gives an overview of the rest of the automated matching routine: after smoothing the scan with a loess of a very small span, shown in (a), we define a striation mark as a groove or a peak if it exceeds a pre-set threshold (of 0.75$\mu m$; obviously this is a crucial parameter. For more discussion see Figure~\ref{fig:thresholds}). Two lines are defined as a match, if their peak/groove base at the threshold overlaps. If there is no overlap, a peak/groove leads to a mismatch. We then count the number of maximum consecutive matches. In this example, the number of consecutive matching striations (CMS) is fifteen, a very high number indicative of a match between the bullets. For lead bullets, such as this, Biasotti \cite{biasotti:1959} considered four or more consecutive lines to be sufficient evidence of a match. XXX need more references XXX \cite{nichols:2003} XXX what does the paper say? AFTE is so frustrating! XXX }

@@

\hh{XXX Does this give us a way to automatically check for the bottom of the bullet? -- We could try to take two cross sections - maybe 50 or 100 $\mu m$ apart. If they don't match, we need to go a bit higher with the lower cross cut. Attempt at this is shown in Figure~\ref{fig:crosscuts2}.}

>>>>

\paragraph{Horizontal Alignment}
Using (for now) a single crosscut across the surface, we extract the values and remove the class characteristics using a loess fit as before. This enables us to focus on the individual characterists. Striation marks show up in this representations as peaks and valleys. Figure~\ref{fig:cross100} shows lines of the surface crosscut at $x = 100$. A horizontal shift of one of the lines (result shown in (b)) emphasizes the strong similarities.
This horizontal shift is based on the cross-correlation between the two surface crosscuts. Let $f(t)$ and $g(t)$ define the values of the crosscut at $t$, then the cross-correlation between $f$ and $g$ at lag $k$ is defined as
\[
(f * g) (k) = \sum_t f(t+k) g(t),
\]
with suitable defined limits of the summation. % (because variances of $f$ and $g$ do not change, the above equation is proportional to the correlation).

\begin{figure}
<<ccf, echo=FALSE, fig.width = 7, fig.height = 3, out.width = '\\linewidth'>>=
lag <- ccf$lag[which.max(ccf$acf)]
qplot(x=ccf$lag, xend=ccf$lag, y = 0, yend= ccf$acf, geom="segment", colour = I("grey50")) + 
  theme_bw() + ylab("Correlation") + xlab("Lag k") +
  geom_segment(aes(x = lag, xend = lag, y = 0, yend =  max(ccf$acf)), colour="black") + 
  scale_x_continuous(breaks = c(-100, -50, lag, 0, 50, 100),
                     minor_breaks = c(-75,-25,25, 75))
@
\caption{\label{fig:ccf}Cross-correlation between the two crosscuts shown in Figure~\ref{fig:crosscut} at lags between -100 and 100. At a lag of -10 the correlation peaks, indicating the largest amount of agreement between the crosscuts. Figure~\ref{fig:crosscutX} shows the lag-shifted crosscuts.}
\end{figure}

@@

Figure~\ref{fig:match} gives an overview of the rest of the automated matching routine: after smoothing the scan with a loess of a very small span, shown in (a), we define a striation mark as a groove or a peak if it exceeds a pre-set threshold (of 0.75$\mu m$; obviously this is a crucial parameter. For more discussion see Figure~\ref{fig:thresholds}). Two lines are defined as a match, if their peak/groove base at the threshold overlaps. If there is no overlap, a peak/groove leads to a mismatch. We then count the number of maximum consecutive matches. In this example, the number of consecutive matching striations (CMS) is fifteen, a very high number indicative of a match between the bullets. For lead bullets, such as this, Biasotti \cite{biasotti:1959} considered four or more consecutive lines to be sufficient evidence of a match. \hh{XXX need more references XXX \cite{nichols:2003} XXX what does the paper say? AFTE is so frustrating! XXX }

@@

\hh{XXX Does this give us a way to automatically check for the bottom of the bullet? Attempt below} 
By comparing cross sections that are not too far apart -- maybe 25 or 50 $\mu m$ for example -- we get an indication whether the crosscut is in a rapidly changing section, such as in a break-off, or in a stable section, where we can expect to find matches reasonably well. In the approach here, we choose a slightly higher crosscut until we find a section with a stable pattern. This process is shown  in Figure~\ref{fig:crosscuts2} at the example of land 1-1 from barrel 3.
